Demes: a specification for interchanging complex demography

### 2022-04-07 paper.tex
Updating ms, resolving bib conflicts

Each population has a selfing rate and cloning rate assigned to it, where each denotes 
the probability that offspring are generated from one generation to the next by either 
self-fertilisation or cloning of an individual. More specifically, denote the clonal rate by 
$\sigma$ and the selfing rate by $S$. In each population a proportion of offspring 
$\sigma$ reproduce clonally, while $1-\sigma$ reproduce sexually. Within the 
sexually--reproducing offspring, $S$ were born via self--fertilisation while the rest were 
outcrossed. Hence $S$ and $\sigma$ can take any value between zero and one, but 
do not have to sum to one. See \citet{hartfield2016facsexcoal} for more details of the 
mathematical properties of these rates in a coalescent context. \mhcomment{If requested 
I can quickly draw up a schematic diagram to illustrate these partitions.} Note that even if 
$S$, $\sigma$ are set to zero then some residual selfing can occur due to sampling in 
the Wright--Fisher model.

@@

\begin{enumerate}
    \item Selection parameters may be arbitrarily complex.  Different fitness effects in different demes.
          Variation over time.  Etc..
          The specification would become unwieldy and perhaps limiting.
    \item By allowing selfing and cloning, we allow many "standard" models to be considered with "no or little"
          extra effort.
    \item However, by parameterising selfing and cloning as we have, we are assuming that these properties of
          populations at given times can be specified independently from the genetics.
          In other words, mutations that cause selfing to "come and go" are not considered.
          However, consuming software is free to ignore these parameters and model the genetics within
          the framework of a soft selection model.
    \item We don't view these as limitations. Rather, this is what most people are doing most of the time.
          Just now we can finally try to do this part w/fewer errors.
\end{enumerate}

>>>>

Each population has a selfing rate and cloning rate assigned to it, where each denotes 
the probability that offspring are generated from one generation to the next by either 
self-fertilisation or cloning of an individual. More specifically, denote the clonal rate by 
$\sigma$ and the selfing rate by $S$. In each population a proportion of offspring 
$\sigma$ reproduce clonally, while $1-\sigma$ reproduce sexually. Within the 
sexually--reproducing offspring, $S$ were born via self--fertilisation while the rest were 
outcrossed. Hence $S$ and $\sigma$ can take any value between zero and one, but 
can sum to more than one. See \citet{hartfield2016facsexcoal} for more details of the 
mathematical properties of these rates in a coalescent context. \mhcomment{If requested 
I can quickly draw up a schematic diagram to illustrate these partitions.}

@@

\begin{enumerate}
    \item Selection parameters may be arbitrarily complex.  Different fitness effects in different demes.
          Variation over time.  Etc..
          The specification would become unwieldy and perhaps limiting.
    \item By allowing selfing and cloning, we allow many "standard" models to be considered with "no or little"
          extra effort. \mhcomment{Plus something on how programs deal with residual selfing.}
    \item However, by parameterising selfing and cloning as we have, we are assuming that these properties of
          populations at given times can be specified independently from the genetics.
          In other words, mutations that cause selfing to "come and go" are not considered.
          However, consuming software is free to ignore these parameters and model the genetics within
          the framework of a soft selection model.
    \item We don't view these as limitations. Rather, this is what most people are doing most of the time.
          Just now we can finally try to do this part w/fewer errors.
\end{enumerate}
